% \bibitem[BiCS(2018a)]{bics-bsp-report-template}
% \newblock {BiCS Bachelor Semester Project Report Template}.
% \newblock {https://github.com/nicolasguelfi/lu.uni.course.bics.global}
% \newblock {University of Luxembourg, BiCS - Bachelor in Computer Science (2017).}

%\bibitem[BiCS(2018b)] {bics-bsp-reference-document}
%{Bachelor in Computer Science}:
%\newblock {BiCS Semester Projects Reference Document}.
%\newblock Technical report, University of Luxembourg (2018)
%
%\bibitem[Armstrong and Green(2017)]{armstrong2017guidelinesforscience}
%J~Scott Armstrong and Kesten~C Green.
%\newblock Guidelines for science: Evidence and checklists.
%\newblock \emph{Scholarly Commons}, pages 1--24, 2017.
%\newblock {https://repository.upenn.edu/marketing_papers/181/}

\bibitem{udemy-tutorial}
\newblock{Introduction to Cloud Computing.}
\newblock{\url{https://bics.udemy.com/introduction-to-cloud-computing/learn/v4/overview}}

\bibitem{coursera-fundamentals}
\newblock{Google Cloud Platform Fundamentals.}
\newblock{\url{https://www.coursera.org/learn/gcp-fundamentals/home/welcome}}

\bibitem{coursera-infrastructure}
\newblock{Google Cloud Platform Infrastructure Foundation.}
\newblock{\url{https://www.coursera.org/learn/gcp-infrastructure-foundation/home/welcome}}

\bibitem{GCP-connect}
\newblock{Connecting to instances.}
\newblock{\url{https://cloud.google.com/compute/docs/instances/connecting-to-instance}}

\bibitem{GCP-project}
\newblock{Creating and Managing Projects.}
\newblock{\url{https://cloud.google.com/resource-manager/docs/creating-managing-projects}}

\bibitem{GCP-instance}
\newblock{Virtual Machine Instances}
\newblock{\url{https://cloud.google.com/compute/docs/instances/}}

\bibitem{IAAS}
\newblock{What is IaaS?}
\newblock{\url{https://azure.microsoft.com/en-us/overview/what-is-IaaS/}}

\bibitem{ssh-tutorial-1}
\newblock{Configure SSH key based authentication.}
\newblock{\url{https://www.digitalocean.com/community/tutorials/how-to-configure-ssh-key-based-authentication-on-a-linux-server}}

\bibitem{ssh-tutorial-2}
\newblock{SSH Key.}
\newblock{\url{https://www.ssh.com/ssh/key/}}

\bibitem{ssh-tutorial-3}
\newblock{Set up SSH public-key authentication.}
\newblock{\url{https://kb.iu.edu/d/aews}}

\bibitem{ISO-IEC}
\newblock{ISO/IEC 25010:2011.}
\newblock{System and Software Quality Models}

% vim: nowrap tw=0
