The tutorials allowed us to understand the core concepts of the
platform and how they relate to each other. This understanding is
materialised in the glossary shown next.

\begin{enumerate}

	\item \textbf{Projects} GCP projects form the basis for creating,
	enabling, and using all GCP services including managing APIs,
	enabling billing, adding and removing collaborators, and managing
	permissions for GCP resources.\cite{GCP-project}
	
	For our sole purpose of creating remote virtual machines, we
	needed to create a project in which to create those.  Added to
	this, we can set project-wide settings that will affect a lot of
	things, including virtual machines, that are contained within it.
	For example, we have a project in which we set a \textit{default
	user} that should be used for SSH connections.  That way we do not
	need to specify explicitly it for every instance. So you can
	consider projects as a sort of working environment.

	\item \textbf{Instance} is a virtual machine hosted on
	Google's infrastructure.\cite{GCP-instance}

	\item \textbf{Billing} is an important part of GCP because the
	services are not provided for free. Contrary to a lot of services
	out there, we do not have to pay a fixed monthly subscription fee
	to use them. The way it works for cloud computing in general is
	that you pay for what you use. What this means is that if you have
	a bunch of instances, which obviously require resources to run,
	and they are \emph{not} running, or in other words: they are shut
	down, then you do not pay for them. If you have instances that are
	running, then the amount you pay mainly depends on the resources
	the instance uses. You may even get discounts in specific cases. 

	\item \textbf{IaaS} is an instant computing infrastructure,
	provisioned and managed over the internet. It’s one of the four
	types of cloud services, along with SaaS, PaaS, and
	serverless.\cite{IAAS} We did not touch on the the last one.
	
	This is a concept that has been touched upon in the
	tutorials along side the other service models. As we have seen
	before, these are part of cloud computing. IaaS is important here
	because using GCP means that we rely on such a service.
	Essentially, Google provides us with the hardware and some
	software that comes with a chosen OS, so in other words the
	infrastructure, which we get to decide how to use.
	 
\end{enumerate}
