% Due to time constraints, we are not going to use the Excalibur
% Tutorial as our test case. Instead, we will do a few basic tasks to
% check if the machine is usable.

% We are going to download and install Remarkable for this purpose.
% Since downloading and installing software will be part of the tasks
% required to set up Excalibur, this seems like a good trade off.

% Further, to make this test case more adapted to a real life situation,
% we will be running one or two Youtube videos in the background as well
% as having a word editor opened while doing the installation.

% If we give our machine enough resources to work properly, then these
% tasks should be doable without any major problems.

We will evaluate the solution with regards to the non-functional
requirements to check how well these have been tackled. Admittedly,
the only part of the final solution that has not been solved yet is to
automatically ensure SSH and RDP\footnote{Remote Desktop Protocol is
used for sharing the Desktop of the instance} access once the instance
is created.  So this is a step which the DevOps engineer needs to do
manually before being able to respectively provision the machine and
set up the Excalibur Environment.

Also, we will consider that the DevOps engineer uses the solution
provided on GitHub more than once since the first time around there
are quite a few things to set up but after that, the deployment of new
instances is quite fast. So for the evaluation we will not consider
the things you have to do the very first time.

We will use the following scale ranging from handled the worst to
handled the best for evaluation purposes: \verb|--|, \verb|-|,
\verb|+|, \verb|++|.

\begin{enumerate}

	\item \textbf{Operability}.  In order to evaluate
	this we will take into consideration all the things the DevOps
	engineer must be able to do beforehand in order to tackle the
	given solution.

	For our solution, the DevOps engineer must at least know how to
	set up GCP and a project, how to set up the gcloud command line
	tool and how to get SSH access to the instances. After that, the
	scripts handle pretty much everything. Granted, the tutorial we
	provided gives step by step instructions for these tasks. Thus we
	conclude that the operability is \verb|+|.

	\item \textbf{Efficiency}. In order to evaluate
	this non-functional requirement, we will look at the amount of
	steps necessary to acquire the Virtual Machine and get them ready
	for the Excalibur Environment. We will orient ourselves on the
	tutorial that will be presented along side the script.

	If you want to create the virtual machine manually it will take
	you 3 steps. If you opt for the script or gcloud tool there is
	only 1 step. Although the gcloud tool might take you a few more
	steps to find the right things to put in the flags.

	For provisioning you have to set up SSH access manually and
	afterwards you need to set up RDP access as well. These two steps
	might be a little cumbersome. So the efficiency is \verb|+|.

	\item \textbf{Satisfaction}.  In order to evaluate
	this, we will again look at the amount of steps necessary but also
	at the time required to execute them.  This is due to the fact
	that more and lengthy steps to follow decrease the ease and speed
	at which you can repeat a given solution.

	We have two steps on SSH and RDP that need to be done manually and
	that may be a little annoying, but at the same time we give the
	user the possibility to use an Excalibur Environment with great
	ease. In fact, the Excalibur user does not have to do anything at
	all. Despite the two manual interactions we will say, thanks to
	the great satisfaction on the user's side, that satisfaction is
	\verb|++|.

	\item \textbf{Maintainability}.  For evaluation of this
	non-functional requirement, we look at how difficult and how much
	effort it may take for the DevOps engineer to tweak the creation
	and provisioning.

	The two steps that require manual intervention, namely the SSH and
	RDP setup, do not give rise to maintainability issues because you
	set them up once and there is nothing to worry about anymore.
	Added to the fact that everything is handled by scripts which you
	can go and edit, we conclude that maintainability is \verb|++|.

	\item \textbf{Reliability}.  For our evaluation purpose, we will
	try to look at how many things can go wrong during the Virtual
	Machine creation as well as setting up remote access. So the fewer
	things there are that can go wrong, the more reliable the solution
	will be.

	Except for the two steps in setting up SSH and RDP nothing can
	really go wrong because the script handles the rest and we are
	granted with a certain level of reliability, concerning the
	virtual machines, on GCP's part. For setting up SSH there are not
	too many things that can go wrong considering there are not a lot
	of steps and they are rather simple. However the RDP setup
	requires a few steps that may or may not demand a little more
	attention, since you need to have a look at one or the other
	configuration file.  Hence we will say that reliability is
	\verb|+|.

	\item \textbf{Adaptability}. To evaluate this non-functional
	requirement, we will consider the ease with which you can adapt an
	instance to a given situation.
	
	Due to the fact that instances are not physical, we can pretty
	easily tweak their properties. We should note that this is not as
	easily accomplished with physical machines as with virtual
	machines. Hence adaptability is \verb|++|.

	\item \textbf{Performance efficiency}. For evaluation purpose, we
	will look at how good of a performance we can achieve with a given
	set of resources.

	Thanks to the fact that we can tweak the instance's
	properties\footnote{We are assuming that the servers where our
	instances are running on have enough resources to allow us to do
	this}, like resources, we have the ability to try and fiddle
	around with the amount of resources until we find a specification
	that yields the greatest performance with the least amount of
	resources. Due to the potential fiddling, we will say that
	performance efficiency is \verb|+|.

\end{enumerate}

The summary table \ref{tab:NFR} gives an overview of this
non-functional requirement evaluation.

\begin{table}
\centering
\begin{tabular}{l | c}
		 Non-Functional Requirement & Evaluation \\\hline
		 Operability & \verb|+| \\
		 Efficiency & \verb|+| \\
		 Satisfaction & \verb|++| \\
		 Maintainability & \verb|++| \\
		 Reliability & \verb|+| \\
		 Adaptability & \verb|++| \\
		 Performance efficiency & \verb|+|
	\end{tabular}
	\caption{NFR summary table}
	\label{tab:NFR}
\end{table}
