The main techical deliverable for this BSP, is a solution that
automates the process of creating and provisioning virtual machines on
the Google Cloud Platform in order to host an Excalibur Environment on
it. Part of this solution is based on earlier results that have been
worked out in the previous semester. 

However, due to time constraints we were not able to fully realise
this objective. So we left out the very last part where you actually
have to install and set up the Excalibur Environment. We know for a
fact that this should not be an issue thanks to the work done in the
previous semester.

The functional requirement of this solution is to set up a new
Excalibur Environment as fast as possible while needing the least
amount of effort. We want as much of the set up as possible to be done
by simply executing the provided scripts.

The non-functional requirements are more numerous. We want to tackle:
\begin{enumerate}

	\item \textbf{Operability}\cite{ISO-IEC}, which determines how
	accessible and easy to use the solution is.

	\item \textbf{Efficiency}\cite{ISO-IEC}, which considers the
	amount of effort necessary to bring the solution to use.
		
	\item \textbf{Satisfaction}\cite{ISO-IEC}, informs us on the
	degree to which user needs are satisfied when a product or system
	is used in a specified context of use.
		
	
	\item \textbf{Maintainability}\cite{ISO-IEC}, considers the ease
	at which the developer can change aspects of the Virtual Machine
	creation and the provisioning.
		
	\item \textbf{Reliability}\cite{ISO-IEC}, tells us whether or not
	our solution is reliable. In other words: Does it give the same
	result in successive trials?

	\item \textbf{Adaptability}\cite{ISO-IEC}, considers the degree to
	which a product or system can effectively and efficiently be
	adapted for different or evolving hardware, software or other
	operational or usage environments.

	\item \textbf{Performance efficiency}\cite{ISO-IEC}, considers the
	the performance relative to the amount of resources used under
	stated conditions to evaluate this non-functional requirement.

		
\end{enumerate}

This technical deliverable is targeted towards a DevOps engineer, who
is in charge of setting up these machines. The Excalibur user should
not have to deal with anything regarding the production of the final
product, namely the Excalibur Environment.

